Further Evidence of Modified Spin-down in Sun-like Stars:\\Pileups in the Temperature--Period Distribution

### 2022-04-18 src/ms.tex
minor edits

We compared the \teff--\prot distribution of the CKS and \edit1{\lamostmcq} samples with the theoretical predictions of \citet{vanSaders2019}, \edit1{which were updated for \citet{Hall2021} and utilized in that work}. Those authors presented forward modeling simulations of the observed Kepler \prot distribution including theoretical models of stellar angular momentum evolution (for both the standard spin-down and WMB scenarios), a galactic population model, and a prescribed observational selection function. \edit1{For this exercise we selected main-sequence stars from the simulations using an evolutionary state flag, defining main-sequence stars as those with a He core mass fraction $<$0.0002.\footnote{These models are packaged in a Zenodo repository at \url{https://doi.org/10.5281/zenodo.6391526
}.}} \edit1{We did not apply a cut on Rossby number to the models to mimic a detection threshold, as one might expect if detectability is Ro-dependent. The issue of detection bias is discussed further in \S\ref{subsec:detectionbias}.}

>>>>

We compared the \teff--\prot distribution of the CKS and \edit1{\lamostmcq} samples with the theoretical predictions of \citet{vanSaders2019}, \edit1{which were updated for \citet{Hall2021} and utilized in that work}. Those authors presented forward modeling simulations of the observed Kepler \prot distribution including theoretical models of stellar angular momentum evolution (for both the standard spin-down and WMB scenarios), a galactic population model, and a prescribed observational selection function. \edit1{For this exercise we selected main-sequence stars from the simulations using an evolutionary state flag, defining main-sequence stars as those with a He core mass fraction $<$0.0002.\footnote{These models are packaged in a Zenodo repository at \url{New URL TBD
}.}} \edit1{We did not apply a cut on Rossby number to the models to mimic a detection threshold, as one might expect if detectability is Ro-dependent. The issue of detection bias is discussed further in \S\ref{subsec:detectionbias}.}
